An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2024-04-16 Cover Letter/main.tex
update for JAFR submission

\hfill
\begin{tabular}{l @{}}
	$29^{th}$ October, 2023\\ % Date
	\textbf{Bryce Ronald William Polley $|$ PhD Candidate}\\
	Queensland University of Technology \\
	School of Mathematical Sciences\\~\\
	Address: Level 8 Y Block, 2 George Street, \\
	Brisbane, Queensland, Australia, 4000\\
	Phone: +61 400 310 105 \\
	Email: bryce.polley@awri.com.au
\end{tabular}

@@

\begin{tabular}{@{} l}
	\textbf{Editors,}\\
	Journal of Economic Geography\\
\end{tabular}

@@

Dear Editor,
\\~\\
\parskip % Vertical whitespace

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\centering \textbf{Submission of Manuscript for Consideration by \\Journal of Economic Geography}\\
\bigskip % Vertical whitespace
\justifying
\noindent

\bigskip \noindent% Vertical whitespace
We wish to submit a new manuscript entitled  ''\textit{An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards}'' for your consideration by the Journal of Economic Geography.
\newline \noindent
In this manuscript we explore the contributing factors to Australian vineyards' operational costs and revenue. We provide insights into the interrelatedness of the factors contributing to operational cost and revenue. We further explore the relationships between these factors and regional differences; showing how different regional effects impact on vineyard operations and outcomes. We use a novel, extensive nationwide data from Australia, collected over a decade by Sustainable Winegrowing Australia. We construct and analyse several models of the multifaceted, multi-resource nature of vineyard management.
\newline \noindent
We believe that this manuscript is appropriate for publication by the Journal of Economic  Geography as it demonstrates the regional differences in operational costs and revenue of Australian vineyards. We further link these outcomes to contributing factors to rank the relative importance of different vineyard activities and resource use; illustrating the economic outcomes of Australian vineyards and linking it to different regional factors. Thank you for your consideration of this manuscript.
\bigskip 
\newline \noindent% Vertical whitespace
\includegraphics[scale=0.1]{signature_block.png}
\newline \noindent
Bryce Polley (corresponding author) on behalf of all coauthors: Kate Helmsted, Mardi Longbottom, Madeline Mitchell, Kerrie Mengersen\\
\newline \noindent
\textit{Corresponding Author}, \textit{Queensland University of Technology}

>>>>

\hfill
\begin{tabular}{l @{}}
	$16^{th}$ April, 2024\\ % Date
	\textbf{Bryce Ronald William Boyd $|$ PhD Candidate}\\
	Queensland University of Technology \\
	School of Mathematical Sciences\\~\\
	Address: Level 8 Y Block, 2 George Street, \\
	Brisbane, Queensland, Australia, 4000\\
	Phone: +61 400 310 105 \\
	Email: bryce.polley@awri.com.au
\end{tabular}

@@

\begin{tabular}{@{} l}
	\textbf{Dr. John P. Brooks and Professor Yangchao Luo,}\\ Editors-in-Chief \\ Journal of Agriculture and Food Research
\end{tabular}

@@

Dear Editors,
\\~\\
\parskip % Vertical whitespace

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\centering \textbf{Submission of Manuscript for Consideration by \\Journal of Agriculture and Food Research}\\
\bigskip % Vertical whitespace
\justifying
\noindent

\bigskip \noindent% Vertical whitespace
We wish to submit a new manuscript entitled  ''\textit{An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards}'' for your consideration by the Journal of Agriculture and Food Research.
\newline \noindent
In this manuscript we explore the contributing factors to Australian vineyards' operational costs and revenue. We provide insights into the interrelatedness of the factors contributing to operational cost and revenue, we further explore the relationships between these factors and regional differences; showing how different regional effects impact on vineyard operations and outcomes. We use a novel, extensive nationwide data from Australia, collected over a decade by Sustainable Winegrowing Australia. We construct and analyse several models of the multifaceted, multi-resource nature of vineyard management.
\newline \noindent
We believe that this manuscript is appropriate for publication by the Journal of Agriculture and Food Research as it demonstrates the regional differences in operational costs and revenue of Australian vineyards and further link these outcomes to contributing factors to rank the relative importance of different vineyard activities and resource use. We illustrate the economic outcomes of Australian vineyards and link these outcomes to different regional factors. Thank you for your consideration of this manuscript.
\bigskip 
\newline \noindent% Vertical whitespace
\includegraphics[scale=0.1]{signature_block.png}
\newline \noindent
Bryce Boyd (corresponding author) on behalf of all coauthors: Kate Helmstedt, Mardi Longbottom, Kerrie Mengersen\\
\newline \noindent
\textit{Corresponding Author}, \textit{Queensland University of Technology}

### 2024-04-16 article.tex
fixed reference error in appendix
update for JAFR submission

@@

\begin{document}
\begin{linenumbers}
\begin{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%       Start Matter      %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%       addressline={},
%%       city={},
%%       postcode={},
%%       state={},
%%       country={}}
%%
%% \affiliation[label2]{organization={},
%%       addressline={},
%%       city={},
%%       postcode={},
%%       state={},
%%       country={}}
%\affiliation[label1]{organization={QUT},
% addressline={},
% city={},
% postcode={},
% state={QLD},
% country={}}
%\affiliation[label2]{organization={AWRI},
% addressline={},
% city={},
% postcode={},
% state={SA},
% country={}}
%\affiliation[label3]{organization={Food Agility CRC},
% addressline={},
% city={},
% postcode={},
% state={Vic},
% country={}}
\author[label1,label2,label3]{Author}
\date{02/08/2023}

@@

%\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
%\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC{} 0000 \sep{} 1111
%\end{keyword}
%%Research highlights
% \begin{highlights}
%  \item Highlight 1
%  \item Highlight 2
%  \item Highlight 3
%  \item Highlight 4
% \end{highlights}
\end{frontmatter}

@@

Table \ref{tab:cont_vars} below shows the ranges of each of the continuous variables:
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \caption{Summary statistics of continuous variables used in XGBoost models.}\label{tab:cont_vars}
  \resizebox{\textwidth}{!}{\begin{tabular}{@{}lllllllll@{}}
  \toprule
   & count & mean & std & min & 0.25 & 0.5 & 0.75 & max \\ \midrule
  Vineyard Solar & 622 & 22916.89 & 104808 & 1 & 1170.75 & 5500 & 14866.25 & 2300000 \\
  Biodiesel & 25 & 6635.932 & 11768.832104 & 1 & 200 & 500 & 10000 & 37216 \\
  Fungicide Spray & 2260 & 7.724801 & 3.279794 & 1 & 6 & 7 & 9 & 68 \\
  LPG & 958 & 327.831399 & 861.538804 & 1 & 40 & 95.835 & 240 & 11950 \\
  Petrol & 4309 & 825.276809 & 1556.621119 & 1 & 135 & 306.66 & 903 & 38568 \\
  Insecticide Spray & 1092 & 1.707189 & 1.316042 & 0 & 1 & 1 & 2 & 12 \\
  Water Used & 5846 & 7301838 & 558206600 & 0.0007 & 13.2655 & 43 & 146.875 & 42680000000 \\
  Fertiliser & 795 & 91149.89 & 483913.4 & 1 & 560 & 4759.5 & 45148.5 & 11358000 \\
  Diesel & 5585 & 11677.070183 & 24380.588742 & 0.1267 & 1240 & 3850 & 12500 & 591000 \\
  Yield & 5935 & 772.902449 & 2175.113895 & 0.03 & 68 & 192.3 & 601.8795 & 72305 \\
  Herbicide Spray & 2026 & 2.646199 & 2.598899 & 0 & 2 & 2 & 3 & 103 \\
  Slashing & 2290 & 3.311485 & 1.826788 & 1 & 2 & 3 & 4 & 26 \\
  Electricity & 1014 & 58223.07 & 177626.3 & 0.019 & 2160 & 9637 & 36498.25 & 3000000 \\
  Area Harvested & 6049 & 66.52604 & 133.4525 & 2.220446E-16 & 10.13 & 24.5 & 66.8 & 2436.15 \\
  Grape Revenue & 875 & 377972 & 606286.8 & 1 & 76000 & 172964 & 386747 & 5700000 \\
  Operating Costs & 853 & 314187.1 & 511522.6 & 1 & 57315 & 140000 & 327408 & 4482828 \\ \bottomrule
  \end{tabular}}
  \end{table}
\clearpage

@@

  \subsection{Irrigation Energy Type}
Below, Table \ref{irig_energy} shows the different types of energy used to power vineyards and their frequency.

@@

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{year.pdf}}
  \caption{Decision tree predicting Year. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:year_tree}
 \end{figure}

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{year.png}}
  \caption{The left-hand side depicts the 10 most relative important variables in predicting Year using XGBoost as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:year_sankey}
 \end{figure}

@@

\begin{figure} 
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.pdf}}
  \caption{Decision tree predicting revenue. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:revenue_tree}
 \end{figure}

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.png}}
  \caption{The left-hand side depicts the 10 most relative important variables in predicting revenue using XGBoost as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:profit}
 \end{figure}

Predictions of profit perfomed poorly compared to operating cost and revenue with an average $R^2$ of 0.2535 and standard deviation of 0.3126. With the large standard deviation being indicative of how unstable the models created were.

>>>>

\let\today\relax
\makeatletter
\def\ps@pprintTitle{%
    \let\@oddhead\@empty
    \let\@evenhead\@empty
    \def\@oddfoot{\footnotesize\itshape
         {Submitted preprint to Journal of Agricultural and Food Research} \hfill\today}%
    \let\@evenfoot\@oddfoot
    }
\makeatother

@@

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%       Start Matter      %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%       addressline={},
%%       city={},
%%       postcode={},
%%       state={},
%%       country={}}
%%
%% \affiliation[label2]{organization={},
%%       addressline={},
%%       city={},
%%       postcode={},
%%       state={},
%%       country={}}
%\affiliation[label1]{organization={QUT},
% addressline={},
% city={},
% postcode={},
% state={QLD},
% country={}}
%\affiliation[label2]{organization={AWRI},
% addressline={},
% city={},
% postcode={},
% state={SA},
% country={}}
%\affiliation[label3]{organization={Food Agility CRC},
% addressline={},
% city={},
% postcode={},
% state={Vic},
% country={}}
% \author[label1,label2,label3]{Author}
% \date{02/08/2023}

@@

%\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
%\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC{} 0000 \sep{} 1111
%\end{keyword}
%%Research highlights
% \begin{highlights}
%  \item Highlight 1
%  \item Highlight 2
%  \item Highlight 3
%  \item Highlight 4
% \end{highlights}
% \fntext[fn1]{This is the first author footnote.}
\end{frontmatter}

@@

Table \ref{tab:cont_vars} below shows the ranges of each of the continuous variables:
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[htb]
  \caption{Summary statistics of continuous variables used in XGBoost models.}\label{tab:cont_vars}
  \resizebox{\textwidth}{!}{\begin{tabular}{@{}lllllllll@{}}
  \toprule
   & count & mean & std & min & 0.25 & 0.5 & 0.75 & max \\ \midrule
  Vineyard Solar & 622 & 22916.89 & 104808 & 1 & 1170.75 & 5500 & 14866.25 & 2300000 \\
  Biodiesel & 25 & 6635.932 & 11768.832104 & 1 & 200 & 500 & 10000 & 37216 \\
  Fungicide Spray & 2260 & 7.724801 & 3.279794 & 1 & 6 & 7 & 9 & 68 \\
  LPG & 958 & 327.831399 & 861.538804 & 1 & 40 & 95.835 & 240 & 11950 \\
  Petrol & 4309 & 825.276809 & 1556.621119 & 1 & 135 & 306.66 & 903 & 38568 \\
  Insecticide Spray & 1092 & 1.707189 & 1.316042 & 0 & 1 & 1 & 2 & 12 \\
  Water Used & 5846 & 7301838 & 558206600 & 0.0007 & 13.2655 & 43 & 146.875 & 42680000000 \\
  Fertiliser & 795 & 91149.89 & 483913.4 & 1 & 560 & 4759.5 & 45148.5 & 11358000 \\
  Diesel & 5585 & 11677.070183 & 24380.588742 & 0.1267 & 1240 & 3850 & 12500 & 591000 \\
  Yield & 5935 & 772.902449 & 2175.113895 & 0.03 & 68 & 192.3 & 601.8795 & 72305 \\
  Herbicide Spray & 2026 & 2.646199 & 2.598899 & 0 & 2 & 2 & 3 & 103 \\
  Slashing & 2290 & 3.311485 & 1.826788 & 1 & 2 & 3 & 4 & 26 \\
  Electricity & 1014 & 58223.07 & 177626.3 & 0.019 & 2160 & 9637 & 36498.25 & 3000000 \\
  Area Harvested & 6049 & 66.52604 & 133.4525 & 2.220446E-16 & 10.13 & 24.5 & 66.8 & 2436.15 \\
  Grape Revenue & 875 & 377972 & 606286.8 & 1 & 76000 & 172964 & 386747 & 5700000 \\
  Operating Costs & 853 & 314187.1 & 511522.6 & 1 & 57315 & 140000 & 327408 & 4482828 \\ \bottomrule
  \end{tabular}}
  \end{table}
\clearpage

@@

  \subsection{Irrigation Energy Type}
Below, Table \ref{tab:irig_energy} shows the different types of energy used to power vineyards and their frequency.

@@

 \begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{year.pdf}}
  \caption{Decision tree predicting Year. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:year_tree}
 \end{figure}

\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{year.png}}
  \caption{The left-hand side depicts the 10 most relative important variables in predicting Year using XGBoost as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:year_sankey}
 \end{figure}

@@

 \begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.pdf}}
  \caption{Decision tree predicting revenue. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:revenue_tree}
 \end{figure}

\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.png}}
  \caption{The left-hand side depicts the 10 most relative important variables in predicting revenue using XGBoost as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:profit}
 \end{figure}

Predictions of profit performed poorly compared to operating cost and revenue with an average $R^2$ of 0.2535 and standard deviation of 0.3126. With the large standard deviation being indicative of how unstable the models created were.
